DRAFT\\Satisfiability Modulo Theories Competition (SMT-COMP) 2014: Rules and Procedures

### 2014-05-08 rules/rules14.tex
Fixing language about solver input.

@@

\header{Input and Output.}
%
Participating solvers must read a single benchmark script presented on its standard input
channel. The script is in the concrete syntax of the SMT-LIB format,
version 2.0, though with a restricted set of commands.   A
\textbf{benchmark script} is just a text file containing a sequence of SMTLIBv2 commands in which:

@@

The main track competition will consist of selected benchmarks in each of the
logic divisions.
Each benchmark script will be presented to the standard input of the solver.
Each SMT-COMP entrant is then expected to attempt to report on its
standard output channel whether the formula is satisfiable
(``\texttt{sat}'', in lowercase, without the quotation marks) or unsatisfiable
(``\texttt{unsat}'').  An entrant may also report ``\texttt{unknown}''
to indicate that it cannot determine satisfiability of the formula.

@@

The application track evaluates SMT solvers when interacting
with an external verification framework, \eg, a model
checker. This interaction, ideally, happens by means of an online
communication between the model checker and the solver: the model
checker repeatedly sends queries to the SMT solver, which in turn
answers either \texttt{sat} or \texttt{unsat}.  In this interaction an SMT-solver is
required to accept queries incrementally via its standard input channel.

>>>>

Information about how to configure and upload a solver is contained in the StarExec user guide on its wiki:
\url{https://wiki.uiowa.edu/display/stardev/User+Guide}.

@@

\header{Input and Output.}
%
Participating solvers must read a single benchmark script presented as its first argument.
Note that previous competitions presented benchmarks to a solver on its standard input
channel, and that the application track will send command inputs to the solver's standard input.
Accordingly, solvers are advised to support both input mechanisms.

 The script is in the concrete syntax of the SMT-LIB format,
version 2.0, though with a restricted set of commands.   A
\textbf{benchmark script} is just a text file containing a sequence of SMTLIBv2 commands in which:

@@

The main track competition will consist of selected benchmarks in each of the
logic divisions.
Each benchmark script will be presented to the solver as its first command-line argument.
Each SMT-COMP entrant is then expected to attempt to report on its
standard output channel whether the formula is satisfiable
(``\texttt{sat}'', in lowercase, without the quotation marks) or unsatisfiable
(``\texttt{unsat}'').  An entrant may also report ``\texttt{unknown}''
to indicate that it cannot determine satisfiability of the formula.

@@

The application track evaluates SMT solvers when interacting
with an external verification framework, \eg, a model
checker. This interaction, ideally, happens by means of an online
communication between the model checker and the solver: the model
checker repeatedly sends queries to the SMT solver, which in turn
answers either \texttt{sat} or \texttt{unsat}.  In this interaction an SMT-solver is
required to accept queries incrementally via its {\em standard input channel}.
